Synthetic network and data generation using GeneNetWeaver(GNW)

### 2016-02-29 code/Rmd/synNetGen.Rmd
Added special ACL privileges to gold standard

      # Store data in synapse
      write.table(tmp, file = paste0('Expression_',x,'.tsv'), sep = '\t', row.names=F, quote=F)
      OBJ = File(paste0('Expression_',x,'.tsv'), 
                 name = paste('Expression',x), 
                 parentId = subFolder$properties$id)
      OBJ = synStore(OBJ, activityName = activityName,
                     executed = thisFile, activityDescription = activityDescription)
    }, data, SUB.FOLD)
    system('rm ecoli*')
  }
}
```

>>>>

      # Store data in synapse
      write.table(tmp, file = paste0('Expression_',x,'.tsv'), sep = '\t', row.names=F, quote=F)
      OBJ = File(paste0('Expression_',x,'.tsv'), 
                 name = paste('Expression',x), 
                 parentId = subFolder$properties$id)
      OBJ = synStore(OBJ, activityName = activityName,
                     executed = thisFile, activityDescription = activityDescription)
    }, data, SUB.FOLD)

    OBJ = File(paste0(tools::file_path_sans_ext(fnames), '.tsv'),
               name = 'Gold Standard', parentId = SUB.FOLD$properties$id)
    OBJ = synStore(OBJ, activityName = activityName, executed = thisFile, activityDescription = activityDescription)

    # Set private acl to the gold standard file
    resAcc = ResourceAccess(principalId = 3319864, 
                            accessType = c('CREATE', 'READ', 'UPDATE', 'DELETE', 'CHANGE_PERMISSIONS', 'DOWNLOAD', 'UPLOAD', 'PARTICIPATE', 'SUBMIT', 'READ_PRIVATE_SUBMISSION', 'UPDATE_SUBMISSION', 'DELETE_SUBMISSION', 'TEAM_MEMBERSHIP_UPDATE', 'SEND_MESSAGE', 'CHANGE_SETTINGS'))
    acl = AccessControlList(id = OBJ$properties$id, resourceAccess = ResourceAccessList(resAcc))
    tmp = synCreateEntityACL(acl)

    system('rm ecoli*')
  }
}
```
